Evaluating infectious disease forecasts with allocation scoring rules

### 2023-12-03 alloscore_manuscript/alloscore-application.Rnw
adding multi-k weighted analysis.

<<ias-comparison, results='asis'>>=
ias <- slim_alloscore_2021.12.20 |>
  group_by(model, K) |>
  summarize(`Allocation score` = sum(components)) |>
  group_by(model) |>
  summarize(IAS = mean(`Allocation score`)) |>
  arrange(IAS)

@@

>>>>

<<ias-comparison, results='asis'>>=
## for visual context
## curve(dnorm(x, mean=15000, sd=3000), from=0, to=30000)
ks <- seq(5000, 25000, by=200)
kprobs <- data.frame(K = ks,
                     weight = dnorm(ks, mean=15000, sd=3000)/sum(dnorm(ks, mean=15000, sd=3000)))

ias <- slim_alloscore_2021.12.20 |>
  group_by(model, K) |>
  summarize(`Allocation score` = sum(components)) |>
  left_join(kprobs) |>
  group_by(model) |>
  summarize(IAS_wt = sum(`Allocation score`*weight, na.rm=TRUE),
            IAS = mean(`Allocation score`)) |>
  arrange(IAS)

@@

p1 <- ggplot(left_join(ias, as), aes(x=AS, y=IAS)) + geom_point(color="blue")
p2 <- ggplot(left_join(ias, as), aes(x=AS, y=IAS_wt)) + geom_point(color="red")

p3 <- slim_alloscore_2021.12.20 |>
  group_by(model, K) |>
  summarize(`Allocation score` = sum(components)) |>
  left_join(kprobs) |>
  ggplot(aes(x=K)) +
  geom_point(aes(y=weight), color = "red") +
  geom_point(y=1/length(unique(slim_alloscore_2021.12.20$K)), color="blue") +
  geom_vline(xintercept = 15000, color="black")

cowplot::plot_grid(p2, p3, p1,
                   nrow=2,
                   align="v",
                   labels = "AUTO")
